Large Scale Marine Protected Areas

### 2019-01-24 docs/tab/main_DID.tex
Updated some figures and tables that had some details. Updated manuscript to send to John

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 12.535$^{***}$ & 12.535$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.021) & (0.021) & (0.041) & (0.013) \\ 
  & & & & & & & & & & \\ 
 Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.232$^{***}$ & 0.232$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
  & & & & & & & & & & \\ 
 Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & $-$0.013 & $-$0.013 & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.047$^{***}$ & $-$0.047$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.272 & 0.272 & 0.081 & 0.283 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Difference-in-differences estimates for our 10 variables of interest: 1) Daily fishing hours, 2) Daily non-fishing at-sea hours, 3) Daily proportion of fishing hours to total at-sea hours, 4) Daily distance traveled, 5) Daily mean distance from port, 6) Daily mean distance from shore, 7) Daily mean distance from port for fishing events, 8) Daily mean distance from shore for fishing events, 9) Monthly proportion of hours spent in Kiribati waters, 10) Monthly proportion of fishing hours spent in PNA waters. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\ 
\hline \\[-1.8ex] 
 Constant & 2.309$^{***}$ & 3.633$^{***}$ & 0.321$^{***}$ & 2.866$^{***}$ & 4.757$^{***}$ & 10.915$^{***}$ & 6.161$^{***}$ & 6.161$^{***}$ & 0.525$^{***}$ & 0.938$^{***}$ \\ 
  & (0.033) & (0.010) & (0.008) & (0.064) & (0.050) & (0.068) & (0.023) & (0.023) & (0.041) & (0.013) \\ 
  & & & & & & & & & & \\ 
 Post & 0.615$^{***}$ & $-$0.223$^{***}$ & 0.142$^{***}$ & 1.354$^{***}$ & $-$0.253$^{***}$ & $-$0.348$^{***}$ & 0.309$^{***}$ & 0.309$^{***}$ & $-$0.024 & $-$0.120$^{***}$ \\ 
  & (0.024) & (0.007) & (0.006) & (0.048) & (0.038) & (0.053) & (0.015) & (0.015) & (0.030) & (0.013) \\ 
  & & & & & & & & & & \\ 
 Treated & $-$0.031 & 0.007 & $-$0.019$^{***}$ & 0.181$^{***}$ & 0.030 & 0.087$^{*}$ & 0.163$^{***}$ & 0.163$^{***}$ & 0.091$^{***}$ & $-$0.028$^{***}$ \\ 
  & (0.026) & (0.006) & (0.007) & (0.053) & (0.034) & (0.050) & (0.017) & (0.017) & (0.030) & (0.008) \\ 
  & & & & & & & & & & \\ 
 Post $\times$ Treated & 0.001 & 0.017$^{**}$ & 0.011 & $-$0.194$^{***}$ & $-$0.036 & $-$0.090 & $-$0.238$^{***}$ & $-$0.238$^{***}$ & 0.006 & 0.066$^{***}$ \\ 
  & (0.028) & (0.008) & (0.007) & (0.056) & (0.044) & (0.061) & (0.018) & (0.018) & (0.034) & (0.014) \\ 
  & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Month FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Flag FE & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 28,067 & 82,242 & 28,067 & 27,239 & 82,716 & 82,716 & 28,067 & 28,067 & 1,645 & 2,289 \\ 
R$^{2}$ & 0.140 & 0.075 & 0.148 & 0.156 & 0.019 & 0.013 & 0.157 & 0.157 & 0.081 & 0.283 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{10}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

### 2019-01-24 docs/tab/sp_corr.tex
Updated some figures and tables that had some details. Updated manuscript to send to John

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 65.538$^{***}$ (5.878) & 0.409$^{***}$ (0.016) \\ 
  Months & 4.429$^{***}$ (0.402) & 0.010$^{***}$ (0.001) \\ 
  Months $^2$ & 0.060$^{*}$ (0.033) & 0.00003 (0.0001) \\ 
  Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
  I(dif$\hat{\mkern6mu}$4) & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 72 & 72 \\ 
R$^{2}$ & 0.741 & 0.631 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

>>>>

\begin{table}[!htbp] \centering 
  \caption{\label{tab:main_DID}Coefficient estimates for a third-polinomial fit to the measures of crowding. The first column shows coefficients for the number of cells with treated and control vessels during the same month. The second column shows coefficients for the spatial correlation for presence / absence of treated and control vessels. The explanatory variable is the number of months before implementation of PIPA. Numbers in parentheses are heteroskedastic-robust standard errors.} 
  \label{} 
\footnotesize 
\begin{tabular}{@{\extracolsep{1pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 Constant & 65.538$^{***}$ (5.878) & 0.409$^{***}$ (0.016) \\ 
  Months & 4.429$^{***}$ (0.402) & 0.010$^{***}$ (0.001) \\ 
  Months $^2$ & 0.060$^{*}$ (0.033) & 0.00003 (0.0001) \\ 
  Months $^3$ & $-$0.004$^{***}$ (0.0004) & $-$0.00001$^{***}$ (0.00000) \\ 
  Months $^4$ & $-$0.0001$^{***}$ (0.00003) & $-$0.00000 (0.00000) \\ 
 \hline \\[-1.8ex] 
Month FE & Yes & Yes \\ 
Flag FE & Yes & Yes \\ 
Observations & 72 & 72 \\ 
R$^{2}$ & 0.741 & 0.631 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}
